\thetitle

### 2021-05-21 writing/discussion.tex
Tweak my previous edits in discussion

The results of the experiment suggests a number of high-level conclusions about
blame strategies in the gradual typed world.  First, run-time type checks have a
large positive impact, regardless of whether these checks assign blame or throw
plain exceptions.  Second, error messages with blame assignments are more
helpful than those without. The results also indicate, though, that blame is not
critical in a majority of cases, and therefore they suggest investigating
whether blame tracking is worth the performance cost.  Third, the Natural
approach fares better than the Transient approach, but only by a small margin.
Since Natural offers complete and sound path-based blame (i.e. it blames all and only those components
that are relevant to a type impedance mismatch) while Transient offers
incomplete but sound heap-based blame~\citep{gfd-oopsla-2019}, the results call
for a study concerning the relative strengths of the two models of blame.
Fourth, given that Transient's sound but shallow run-time type checks do not
seem to hamper debugging, a version of the Natural semantics of Typed Racket
that disables some of its wrappers may offer an answer to the well-known
performance issues of Natural~\citep{gtnffvf-jfp-2019}.  Fifth, given that both
modes of the Transient rational programmer are equally successful and that
Transient-last produces shorter trails, Reticulated Python could limit the size
of blame sequences to the last few entries to reduce its serious performance
problems (see below).

@@

>>>>

The results of the experiment suggests a number of high-level conclusions about
blame strategies in the gradual typed world.  First, run-time type checks have a
large positive impact, regardless of whether these checks assign blame or throw
plain exceptions.  Second, error messages with blame assignments are more
helpful than those without. The results also indicate, though, that blame is not
critical in a majority of cases, and therefore they suggest investigating
whether blame tracking is worth the performance cost.  Third, the Natural
approach fares better than the Transient approach, but only by a small margin.
Since Natural offers complete and sound path-based blame (i.e. it blames all and only those components
that are relevant to a type impedance mismatch) while Transient offers
incomplete but sound heap-based blame~\citep{gfd-oopsla-2019}, the results call
for a study concerning the relative strengths of the two models of blame.
Fourth, given that Transient's sound but shallow run-time type checks do not
seem to hamper debugging, a version of the Natural semantics of Typed Racket
that disables some of its wrappers may offer an answer to the well-known
performance issues of Natural~\citep{gtnffvf-jfp-2019}.  Fifth, the fact that both
modes of the Transient rational programmer are equally successful suggests that
returning the whole blame sequence may not be beneficial. If so, Reticulated
Python could limit the size of blame sequences to attempt to mitigate its
serious performance problems (see below).

@@

%% -----------------------------------------------------------------------------
\subsection{Threat: Is the Definition of Interesting Scenarios Reasonable?} \label{sec:threat:erasure-bias}

Section~\ref{sub:mutate-interesting} defines criteria for interesting mutations,
one of which limits the scenarios under consideration to those with mistakes
that raise a run-time error under Erasure. In other words, the experiment is
Erasure-biased: it only considers the usefulness of blame when the safety checks
of the underlying language alone are sufficient to detect the mistake. In
reality, some mistakes require run-time type checks to be
detected~\cite{gfd-oopsla-2019}, and it is possible that blame has more or less
to offer for these kinds of mistakes. If that is the case, then the results of
the experiment on a population of scenarios including such mistakes should be
different.

In fact, the authors have conducted a variation of the experiment that provides
some preliminary evidence that this difference may be significant. In
particular, the variation of the experiment includes only three of the
benchmarks but broadens the selection of scenarios to include any that raise
run-time errors under Natural, regardless of other semantics. The preliminary
results from this experiment suggest that without Erasure-bias, Natural blame
may be much more useful than all of the other modes.
